---
title: "HHS-Provider-Relief-Fund"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
output:
  html_document:
    css: style.css
    df_print: paged
    theme: darkly
    toc: true
    toc_float: true
    code_folding: hide
---



```{r message=FALSE, warning=FALSE}
library("htmltools")
library("here")
library("dplyr")
library("RSocrata")
library("tidyverse")
library("openxlsx") 
library("googledrive")
library("knitr")
library("wordcloud")
library("RColorBrewer")
library("wordcloud2")
library("DT")
`%notin%` <- Negate(`%in%`)
options(scipen = 999)
source("private.R")

```
# About

HHS is providing support to healthcare providers fighting the coronavirus disease 2019 (COVID-19) pandemic through the bipartisan Coronavirus Aid, Relief, & Economic Security (CARES) Act; the Paycheck Protection Program and Health Care Enhancement Act (PPPHCEA); and the Coronavirus Response and Relief Supplemental Appropriations (CRRSA) Act, which provide a total of $178 billion for relief funds to hospitals and other healthcare providers on the front lines of the COVID-19 response. This funding supports healthcare-related expenses or lost revenue attributable to COVID-19 and ensures uninsured Americans can get treatment for COVID-19. HHS is distributing this Provider Relief Fund (PRF) money and these payments do not need to be repaid.

The Department allocated $50 billion in PRF payments for general distribution to Medicare facilities and providers impacted by COVID-19, based on eligible providers' net reimbursement. HHS has made other PRF distributions to a wide array of health care providers and more information on those distributions can be found here: https://www.hhs.gov/coronavirus/cares-act-provider-relief-fund/data/index.html


https://taggs.hhs.gov/Coronavirus/Providers

https://www.hrsa.gov/provider-relief/

https://data.cdc.gov/Administrative/Claims-Reimbursement-to-Health-Care-Providers-and-/rksx-33p3



# Getting the Data

| **Column Name** | **Column ID** | **Description**                                                                | **Type**   |
| :-------------- | :------------ | :----------------------------------------------------------------------------- | :--------- |
| Provider Name   | provider_name | Provider name associated with the billing TIN to whom the payment was issued.  | Plain Text |
| State           | state         |                                                                                | Plain Text |
| City            | city          |                                                                                | Plain Text |
| Payment         | payment       | The total (cumulative) payment that the provider has received AND attested to. | Plain Text |

```{r HHSProviderReliefFund, cache=TRUE, cache.extra = Sys.Date(), message=FALSE, warning=FALSE}
## Install the required package with:
## install.packages("RSocrata")
library("dplyr")
library("RSocrata")
library("tidyverse")

HHSProviderReliefFund <- read.socrata(
  "https://data.cdc.gov/resource/kh8y-3es6.json"
)
skimr::skim(HHSProviderReliefFund) 
```


```{r}
nrow(HHSProviderReliefFund)
```


```{r}
nrow(HHSProviderReliefFund |> distinct())
```


# Processing the Data


```{r message=FALSE, warning=FALSE}
HHSProviderReliefFund <-
        HHSProviderReliefFund %>% mutate(state = as.factor(state),
                                  city = as.factor(city),
                                  payment_number = as.numeric(( gsub( "[\\$,.]", "", payment)))
                                ) %>%
  select(-payment)



HHSProviderReliefFund <- HHSProviderReliefFund %>% arrange(desc(payment_number))

DT::datatable(head(HHSProviderReliefFund, 1000) )

```







```{r}
HHSProviderReliefFundSummary <- HHSProviderReliefFund %>% group_by(state) %>% summarise(payment_sum = sum(payment_number, na.rm = TRUE) ) %>% arrange(desc(payment_sum))
HHSProviderReliefFundSummary
```



```{r summary, cache=TRUE, cache.extra = Sys.Date(), message=FALSE, warning=FALSE}
summary(HHSProviderReliefFund)
```



# Word Cloud

```{r unit_name_words, cache=TRUE, cache.extra = Sys.Date(), message=FALSE, warning=FALSE}
#install.packages("tm")
library(tm)
#Create a vector containing only the text
text <- HHSProviderReliefFund %>% 
  #head(nrow(HHSProviderReliefFund)/1) %>% 
  select(provider_name)
# Create a corpus  
docs <- Corpus(VectorSource(text))
docs <- docs %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))

dtm <- TermDocumentMatrix(docs) 
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
df <- data.frame(word = names(words),freq=words)

df <- df %>% arrange(desc(freq) )  %>% filter(word %notin% c("llc", "inc", "dds"))

df
```


```{r unit_name_words_cloud, cache=TRUE, cache.extra = Sys.Date(), message=FALSE, warning=FALSE}
set.seed(1234) # for reproducibility 
wordcloud2(data=df, size=1.6, color='random-dark')
```



# Upload Data to Goodle Drive

```{r upload-VendorPayments-Data, message=FALSE, warning=FALSE, cache=TRUE, cache.extra=Sys.Date()}
# drive_auth(email = "jenny@example.com")
# num_groups = 2
# 
# HHSProviderReliefFundSplit <- HHSProviderReliefFund %>% 
#    group_by((row_number()-1) %/% (n()/num_groups)) %>%
#    nest %>% pull(data)
# HHSProviderReliefFundSplit[[1]]
# HHSProviderReliefFundSplit[[2]]

openxlsx::write.xlsx(list("HHS Provider Relief Fund All" = HHSProviderReliefFund) , here("data/HHS Provider Relief Fund All.xlsx"), overwrite = TRUE, asTable = TRUE, freezePane = c("firstRow"), colWidths = "auto", withFilter = TRUE) 

# #googledrive::drive_auth() 
# openxlsx::write.xlsx(list("HHS Provider Relief Fund" = HHSProviderReliefFundSplit[[1]]) , here("data/HHS Provider Relief Fund 1.xlsx"), overwrite = TRUE, asTable = TRUE, freezePane = c("firstRow"), colWidths = "auto", withFilter = TRUE) 
# openxlsx::write.xlsx(list("HHS Provider Relief Fund 2" = HHSProviderReliefFundSplit[[2]]) , here("data/HHS Provider Relief Fund 2.xlsx"), overwrite = TRUE, asTable = TRUE, freezePane = c("firstRow"), colWidths = "auto", withFilter = TRUE) 
# 
# #googledrive::drive_upload(media =here("data/HHS Provider Relief Fund 2.xlsx"),   type = "spreadsheet", overwrite = TRUE) 
# googledrive::drive_update(media =here("data/HHS Provider Relief Fund 1.xlsx"), file = as_id("1Jl41HesB8z21IS4XF9QZ1HpF_ykOR1X_4Linl1jp9WY"))
# 
# googledrive::drive_update(media =here("data/HHS Provider Relief Fund 2.xlsx"), file = as_id("1gRZq4jWkJSJJMFkqo610b-NjEKyigsT3WJBPdn8J6jo"))

googledrive::drive_update(media =here("data/HHS Provider Relief Fund All.xlsx"), file = as_id("1yWozJow3ksgKhi9GjQTnFwLD0Hg2U7jl"))

```
1gRZq4jWkJSJJMFkqo610b-NjEKyigsT3WJBPdn8J6jo



The processed data can be found on [Google Sheets](https://docs.google.com/spreadsheets/d/1Jl41HesB8z21IS4XF9QZ1HpF_ykOR1X_4Linl1jp9WY).


# Present Data in Tableau

The processed data stored in Google Sheets is used in [Tableau Public](https://public.tableau.com/s/) to generate [interactive visualizations](https://public.tableau.com/app/profile/andr.van.zyl/viz/Atlanta_16292337333820/About). 

```{r message=FALSE, warning=FALSE}
includeHTML(path = here("docs/tableau-dashboard.html")) 
```

# Pushing Updates to GitHub

```{r eval=FALSE, include=FALSE}
library(gitcreds)

gitcreds_set()
```

